Evolved disk population of young brown dwarfs in \emph{Ophiuchus}\footnote{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}

### 2015-04-14 chIMACS/ms.tex
document would not compile for unknown reasons, maybe too much math in the short fig caption

\begin{figure}[ht!]
  \caption[$[3.6]-[8.0]$ as a function of spectral type for young stellar and substellar objects]{ Distribution of $[3.6]-[8.0]$ as a function of spectral type for young stellar and substellar objects in this work (white squares with black edges).  The distribution of 187 Class I, II, and III Taurus members with spectral types later than M0 \citep{2010ApJS..186..111L} is shown as the kernel density estimate contours in the background.  The black circles with white edges are the 8 sources towards \emph{Ophiuchus} from \citet{allers06} with spectral types from \citet{2011ASPC..448..633G}.  The white dashed line is constructed from Class III young stellar and substellar objects in $\eta$ Cha, $\epsilon$ Cha, and TWA \citep{2010ApJS..186..111L}, and represents the photospheric colors of young objects.  The two edge-on disks OPH\_2 and OPH\_349 are outliers in this plot.  The two disk-bearing sources are 2mx\_10919 and 2mx\_14856.  The other 12 members are diskless sources.  \label{fig_I1_I4_density} }
\centering
\includegraphics[scale=0.6]{chIMACS/figures/I1_I4_density.pdf}
\end{figure}

>>>>

\begin{figure}[ht!]
  \caption[Mid-infrared slope as a function of spectral type]{Distribution of $[3.6]-[8.0]$ as a function of spectral type for young stellar and substellar objects in this work (white squares with black edges).  The distribution of 187 Class I, II, and III Taurus members with spectral types later than M0 \citep{2010ApJS..186..111L} is shown as the kernel density estimate contours in the background.  The black circles with white edges are the 8 sources towards \emph{Ophiuchus} from \citet{allers06} with spectral types from \citet{2011ASPC..448..633G}.  The white dashed line is constructed from Class III young stellar and substellar objects in $\eta$ Cha, $\epsilon$ Cha, and TWA \citep{2010ApJS..186..111L}, and represents the photospheric colors of young objects.  The two edge-on disks OPH\_2 and OPH\_349 are outliers in this plot.  The two disk-bearing sources are 2mx\_10919 and 2mx\_14856.  The other 12 members are diskless sources.  \label{fig_I1_I4_density} }
\centering
\includegraphics[scale=0.6]{chIMACS/figures/I1_I4_density.pdf}
\end{figure}
